Kit Theory

### 2023-06-21 paper/paper.tex
Update.

\usepackage{tcolorbox}
% \newenvironment{LibCode}{%
%   \begin{tcolorbox}[boxrule=0.5pt,top=0pt,left=0pt,right=2.5pt,boxsep=0pt]\vspace{-0.5\baselineskip}}{%
%   \end{tcolorbox}}
\newenvironment{LibCode}{%
  \begin{tcolorbox}[boxrule=0.0pt,frame hidden,top=0pt,left=0pt,right=2.5pt,boxsep=0pt]\vspace{-0.5\baselineskip}}{%
  \end{tcolorbox}}

@@

  \begin{LibCode}
  \KSortTy
  \end{LibCode}

  \FSort
  \FSyntax
  The variable constructor \texttt{'\_} takes a sorted DeBruijn-index \texttt{S~∋~s}.
  Since the \texttt{Sort}s in \texttt{S} are restricted to the sort-type \texttt{Var}, it is not possible to construct kind-variables.

  \subsection{Library}
  \KVariables
  \KSortTy
  \KTerms
  \subsection{System F}
  \FSort
  \FSyntax
  \FTerms

  \section{Maps}
  \subsection{Library}
  \KKit
  \KMap
  \KAp
  \KExt
  \KLift
  \KId
  \KSingle
  \KWeaken
  \KEq
  \KFunExt
  \KIdLift
  % \KIdLiftProof
  \KKitNotation
  \KTraversal
  \KKitInstances
  \KKitOpen
  \subsection{System F}
  \FTraversalOp
  \FTraversalId
  \FTraversalIdProofInteresting
  % \FTraversalIdProofRest
  \FTraversal

  \section{Map Composition}
  \subsection{Library}
  \KWkKit
  \KWkKitInstances
  \KComposeKit
  \KComposition
  \KComposeKitAp
  % \KComposeKitApProof
  \KDistLiftCompose
  % \KDistLiftComposeProof
  \KComposeKitNotation
  \KComposeTraversal
  \KCommLiftWeaken
  % \KCommLiftWeakenProof
  \KCommLiftWeakenTraverse
  % \KCommLiftWeakenTraverseProof
  \KComposeKitInstances
  \KComposeKitInstancesConcrete
  \KWeakenCancelsSingle
  % \KWeakenCancelsSingleProof
  \KWeakenCancelsSingleTraverse
  % \KWeakenCancelsSingleTraverseProof
  \KDistLiftSingle
  % \KDistLiftSingleProof
  \KDistLiftSingleTraverse
  % \KDistLiftSingleTraverseProof
  \subsection{System F}
  \FAssoc
  \FAssocProofInteresting
  % \FAssocProofRest
  \FComposeTraversal

  \section{Types \& Contexts}
  \subsection{Library}
  \KTypeSorts
  \KTypes
  \KContextHelper
  \KContexts
  \KContextLookup
  \subsection{System F}
  \FTypes

  \section{Typing}
  \subsection{Library}
  \KVariableTyping
  \KTyping
  \KTypingKit
  \KMapTyping
  \KLiftTyping
  % \KLiftTypingProof
  \KSingleTyping
  % \KSingleTypingProof
  \KTypingNotation
  \KTypingTraversal
  \KTypingInstances
  % \KTypingTraversalNotation
  \subsection{System F}
  \FTyping
  \FTypingInst
  \FPreserve
  \FTypingTraversal

  \section{Semantics}
  % \FValues
  \FReduction

  \section{Subject Reduction}
  \FSubjectReduction
  \FSubjectReductionProofInteresting
  % \FSubjectReductionProofRest

>>>>

\usepackage{tcolorbox}

\newenvironment{LibCode*}{%
  \begin{tcolorbox}[%
    colframe=white,%
    boxrule=0.0pt,%
    top=2.5pt,%
    left=2.5pt,%
    bottom=2.5pt,%
    right=2.5pt,%
    boxsep=0pt%
  ]\vspace{-0.2\baselineskip}%
}{%
  \vspace{-1\baselineskip}%
  \end{tcolorbox}%
}

\newcommand*\LibCode[1]{\begin{LibCode*}{#1}\end{LibCode*}}
\newcommand*\AppCode[1]{{#1}}

@@

  \LibCode\KSortTy

  \AppCode\FSort

  \LibCode\KVariables
  \AppCode\FSyntax
  The variable constructor \texttt{'\_} takes a sorted DeBruijn-index \texttt{S~∋~s}.
  Since the \texttt{Sort}s in \texttt{S} are restricted to the sort-type \texttt{Var}, it is not possible to construct kind-variables.

  \subsection{Library}
  \LibCode\KTerms
  \subsection{System F}
  \FSort
  \FSyntax
  \FTerms

  \section{Maps}
  \subsection{Library}
  \LibCode\KKit
  \LibCode\KMap
  \LibCode\KAp
  \LibCode\KExt
  \LibCode\KLift
  \LibCode\KId
  \LibCode\KSingle
  \LibCode\KWeaken
  \LibCode\KEq
  \LibCode\KFunExt
  \LibCode\KIdLift
  % \LibCode\KIdLiftProof
  \LibCode\KKitNotation
  \LibCode\KTraversal
  \LibCode\KKitInstances
  \LibCode\KKitOpen
  \subsection{System F}
  \AppCode\FTraversalOp
  \AppCode\FTraversalId
  \AppCode\FTraversalIdProofInteresting
  % \LibCode\FTraversalIdProofRest
  \AppCode\FTraversal

  \section{Map Composition}
  \subsection{Library}
  \LibCode\KWkKit
  \LibCode\KWkKitInstances
  \LibCode\KComposeKit
  \LibCode\KComposition
  \LibCode\KComposeKitAp
  % \LibCode\KComposeKitApProof
  \LibCode\KDistLiftCompose
  % \LibCode\KDistLiftComposeProof
  \LibCode\KComposeKitNotation
  \LibCode\KComposeTraversal
  \LibCode\KCommLiftWeaken
  % \LibCode\KCommLiftWeakenProof
  \LibCode\KCommLiftWeakenTraverse
  % \LibCode\KCommLiftWeakenTraverseProof
  \LibCode\KComposeKitInstances
  \LibCode\KComposeKitInstancesConcrete
  \LibCode\KWeakenCancelsSingle
  % \LibCode\KWeakenCancelsSingleProof
  \LibCode\KWeakenCancelsSingleTraverse
  % \LibCode\KWeakenCancelsSingleTraverseProof
  \LibCode\KDistLiftSingle
  % \LibCode\KDistLiftSingleProof
  \LibCode\KDistLiftSingleTraverse
  % \LibCode\KDistLiftSingleTraverseProof
  \subsection{System F}
  \AppCode\FAssoc
  \AppCode\FAssocProofInteresting
  % \AppCode\FAssocProofRest
  \AppCode\FComposeTraversal

  \section{Types \& Contexts}
  \subsection{Library}
  \LibCode\KTypeSorts
  \LibCode\KTypes
  \LibCode\KContextHelper
  \LibCode\KContexts
  \LibCode\KContextLookup
  \subsection{System F}
  \AppCode\FTypes

  \section{Typing}
  \subsection{Library}
  \LibCode\KVariableTyping
  \LibCode\KTyping
  \LibCode\KTypingKit
  \LibCode\KMapTyping
  \LibCode\KLiftTyping
  % \LibCode\KLiftTypingProof
  \LibCode\KSingleTyping
  % \LibCode\KSingleTypingProof
  \LibCode\KTypingNotation
  \LibCode\KTypingTraversal
  \LibCode\KTypingInstances
  % \LibCode\KTypingTraversalNotation
  \subsection{System F}
  \AppCode\FTyping
  \AppCode\FTypingInst
  \AppCode\FPreserve
  \AppCode\FTypingTraversal

  \section{Semantics}
  % \AppCode\FValues
  \AppCode\FReduction

  \section{Subject Reduction}
  \AppCode\FSubjectReduction
  \AppCode\FSubjectReductionProofInteresting
  % \FSubjectReductionProofRest
